\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single Transient}

### 2020-03-05 paper/eccv2020/sections/hardware.tex
Added discussion about the the two spad histograms

The monocular depth estimate is calculated
using the RGB image captured by the Kinect v2.
The SPAD records temporal histograms with 4096 bins, each corresponding to a
time window of 16~ps. The SPAD and laser are co-axially aligned using a beam
splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the
combined laser pulse width and SPAD jitter is about 70~ps, allowing the system
to record depth maps with an accuracy of about 1~cm. A National Instruments data
acquisition device (NI-DAQ USB-6343) provides synchronization signals for the
galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a
resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD
measurement is generated by summing all of these measurements for a specific
scene. This allows us to validate the accuracy of the proposed histogram
matching algorithm, which only uses the integrated single histogram, by
comparing it with the captured depth. To empirically assess the equivalence of
diffused SPAD measurements and summed scanned measurements, we captured the
following scene under both raster-scanned and diffuse mode conditions:

>>>>

The monocular depth estimate is calculated
using the RGB image captured by the Kinect v2.
The SPAD records temporal histograms with 4096 bins, each corresponding to a
time window of 16~ps. The SPAD and laser are co-axially aligned using a beam
splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the
combined laser pulse width and SPAD jitter is about 70~ps, allowing the system
to record depth maps with an accuracy of about 1~cm. A National Instruments data
acquisition device (NI-DAQ USB-6343) provides synchronization signals for the
galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a
resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD
measurement is generated by summing all of these measurements for a specific
scene. This allows us to validate the accuracy of the proposed histogram
matching algorithm, which only uses the integrated single histogram, by
comparing it with the captured depth --- \edit{such validation would not be possible if we were to capture measurements with an actual diffused SPAD.}

\edit{To verify that our simulated diffused SPAD measurements are equivalent to measurements produced by an actual diffused SPAD, we setup a system consisting of a diffused and scanned SPAD side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the diffuse SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate the two systems produce near equivalent measurements; the slight differences in their two histograms can be attributed to a baseline difference of about 10cm. That is, they see the scene from slightly different perspectives.
}
